Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-21 resex.tex
One more step in revision of bibliography. Replaced Chamonix reference (not accessible) on 2016 LHC performance with Wenninger at IPAC17. Added Warp reference. Renamed BibTeX file.

\begin{table*}
  \caption{ Stored beam energy for different past, present and future
    colliders. Each new machine represents a leap in stored beam
    energy.}
  \label{tab:stored_energy}
  \begin{ruledtabular}
    \begin{tabular}{lccccc}
      Collider& Tevatron (protons) \cite{tevatron} & LHC 2016 \cite{chamonix2017param}	& LHC nominal \cite{lhc_design} & HL-LHC \cite{hlcdr} & FCC \cite{fcc_param_2017} \\
      \colrule
      Beam energy [TeV] & 0.98 & 6.5 & 7.0 & 7.0 & 50.0\\
      Number of bunches & 36 & 2220 & 2808 & 2748 & ? \\
      Number of particles per bunch & $2.90\times 10^{11}$ & $1.15\times 10^{11}$ & $1.15\times 10^{11}$ & $2.2\times 10^{11}$ & $1.0\times 10^{11}$\\
      Stored beam energy [MJ] & 1.6 & 265.9 & 362.2 & 678.0 & 8400 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=0.4\textwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Emap} &
    \includegraphics[width=0.4\textwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Eslice}\\
  \end{tabular}
  \caption{Calculated relative electric field for the hollow electron
    gun CHG1b in the transverse $x$-$y$ plane (left) and as
    1-dimensional cuts through the $x$ and $y$ axes (right). The field
    calculations are based on measurements at the Fermilab
    electron-lens test stand combined with Warp calculations of the
    electric potentials and fields in a cylindrical beam pipe.}
  \label{core:fig:1}
\end{figure*}

@@

To estimate the dipole component of the kicks that originate from the
injection and extraction bends, we used the approach described in
Ref.~\cite{hel_bends_stancari}. The bends are modeled as a bent
cylindrical pipe with a static charge distribution of electrons. The
resulting electric field is calculated, with the vacuum pipe as
boundary, using the solvers of the Warp particle-in-cell
code~\cite{warp}. (The contribution of the magnetic field generated by
the electron current was neglected in this study.) The field,
integrated over the trajectory of the protons, is then translated into
a symplectic kick map.

@@

For a given HL-LHC HEL configuration, the corresponding
current-density profile measured in the Fermilab test stand is used as
input to calculate the electromagnetic fields. For the purpose of
estimating the residual fields, the measured distribution is
compressed to the inner electron beam radius of 1.24~mm, corresponding
to $4\sigma_p$, as described in Table~\ref{tab:hllhc_param} and
Table~\ref{tab:hel_param}. A distribution with about $65\,000$
particles is generated according to the measured current-density
profile. As boundary condition, the LHC inner beam pipe radius
$b = \q{30}{mm}$ is used. The potential and fields are then calculated
with Warp~\cite{warp}. The resulting relative electric field strengths
are shown in Fig.~\ref{core:fig:1}. The electric field is obviously
proportional to the charge density of electrons. Its relative strength
is rather insensitive to the hollow beam radii, as long as these
remain small compared to the beam pipe radius. Further details on the
measurements and Warp simulations can be found in
Ref.~\cite{hel_res_field_stancari_2017}.

@@

The random excitation is a powerful and flexible halo-cleaning
pattern, but it is also potentially harmful for the proton beam
core. The effects of random noise in various machines have been
studied extensively in the past (see, for instance,
Refs.~\cite{noise_lebedev_ssc, noise_alexahin_lhc, noise_2007_ohmi,
  noise_2014_ohmi}).

@@

% bibliography
\bibliography{resex-bibdesk}

>>>>

\begin{table*}
  \caption{ Stored beam energy for different past, present and future
    colliders. Each new machine represents a leap in stored beam
    energy.}
  \label{tab:stored_energy}
  \begin{ruledtabular}
    \begin{tabular}{lccccc}
      Collider& Tevatron (protons) \cite{tevatron} & LHC 2016 \cite{Wenninger:IPAC:2017}	& LHC nominal \cite{lhc_design} & HL-LHC \cite{hlcdr} & FCC \cite{fcc_param_2017} \\
      \colrule
      Beam energy [TeV] & 0.98 & 6.5 & 7.0 & 7.0 & 50.0\\
      Number of bunches & 36 & 2220 & 2808 & 2748 & ? \\
      Number of particles per bunch & $2.90\times 10^{11}$ & $1.15\times 10^{11}$ & $1.15\times 10^{11}$ & $2.2\times 10^{11}$ & $1.0\times 10^{11}$\\
      Stored beam energy [MJ] & 1.6 & 265.9 & 362.2 & 678.0 & 8400 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

\begin{figure*}
  \begin{tabular}{cc}
    \includegraphics[width=0.4\textwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Emap} &
    \includegraphics[width=0.4\textwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Eslice}\\
  \end{tabular}
  \caption{Calculated relative electric field for the hollow electron
    gun CHG1b in the transverse $x$-$y$ plane (left) and as
    1-dimensional cuts through the $x$ and $y$ axes (right). The field
    calculations are based on measurements at the Fermilab
    electron-lens test stand combined with \code{Warp} calculations of
    the electric potentials and fields in a cylindrical beam pipe.}
  \label{core:fig:1}
\end{figure*}

@@

To estimate the dipole component of the kicks that originate from the
injection and extraction bends, we used the approach described in
Ref.~\cite{hel_bends_stancari}. The bends are modeled as a bent
cylindrical pipe with a static charge distribution of electrons. The
resulting electric field is calculated, with the vacuum pipe as
boundary, using the solvers of the \code{Warp} particle-in-cell
code~\cite{warp, Friedman:IEEE-plasma:2014}. (The contribution of the
magnetic field generated by the electron current was neglected in this
study.) The field, integrated over the trajectory of the protons, is
then translated into a symplectic kick map.

@@

For a given HL-LHC HEL configuration, the corresponding
current-density profile measured in the Fermilab test stand is used as
input to calculate the electromagnetic fields. For the purpose of
estimating the residual fields, the measured distribution is
compressed to the inner electron beam radius of 1.24~mm, corresponding
to $4\sigma_p$, as described in Table~\ref{tab:hllhc_param} and
Table~\ref{tab:hel_param}. A distribution with about $65\,000$
particles is generated according to the measured current-density
profile. As boundary condition, the LHC inner beam pipe radius
$b = \q{30}{mm}$ is used. The potential and fields are then calculated
with \code{Warp}~\cite{warp, Friedman:IEEE-plasma:2014}. The resulting
relative electric field strengths are shown in
Fig.~\ref{core:fig:1}. The electric field is obviously proportional to
the charge density of electrons. Its relative strength is rather
insensitive to the hollow beam radii, as long as these remain small
compared to the beam pipe radius. Further details on the measurements
and \code{Warp} simulations can be found in
Ref.~\cite{hel_res_field_stancari_2017}.

@@

The random excitation is a powerful and flexible halo-cleaning
pattern, but it is also potentially harmful for the proton beam
core. The effects of random noise in various machines have been
studied extensively in the past (see, for instance,
Refs.~\cite{noise_lebedev_ssc, noise_alexahin_lhc, noise_2007_ohmi,
  noise_2014_ohmi, md400_noise_injection}).

@@

% bibliography
\bibliography{resex}
